\DocumentMetadata{
 testphase=phase-II,
 pdfversion=2.0
}


\documentclass[print]{ag-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
%%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%%

% \usepackage{microtype}
\usepackage{fontspec}
\defaultfontfeatures{Mapping=tex-text,Ligatures={NoRequired,NoCommon}}



\addbibresource{agbib.bib} % Specify the bibliography file to include publications


%%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Aaron Gonzales}
\author{Aaron Gonzales}

\makeatletter
\renewcommand\maketitle{
{\raggedright % Note the extra {

{\headingfont \bfseries \@title }{\smallheaderfont~|~aaron@aarongonzales.net~|~505.385.9209 |~github.com/binaryaaron}
}} % Note the extra }
\makeatother
\usepackage[document]{ragged2e}

\begin{document}

\pagenumbering{gobble}
\pagestyle{fancy}
\fancyhf{}
\fancyhead{}
\fancyfoot{}
\cfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\maketitle

\raggedright
\section*{Selected Experience}

\begin{job}
  {}{Staff Machine Learning Engineer}{Mozilla.ai}{April 2023}{current}{Remote, USA}{
    Hired as Lead/Founding Engineer to develop Mozilla.ai's foundational research and development platform.
    

    \begin{myitemize}
      \item Established engineering culture and practice, including coding standards, developer tooling, CI/CD
      pipelines, API design styles, abstraction patterns, and a technical hiring program.

      \item Designed and built a platform for large language model (LLM) research and product iteration on a
      cloud-based GPU cluster. Continued with a small team to iterate and enhance the platform.

      \item Managed procurement, setup, and relationships of cloud and IT vendors.
      \item Coordinated Neurips and KDD workshops \autocite{kdd_2023_workshop,neurips_llm_efficiency_2023}.


    \end{myitemize}
  }
\end{job}


\begin{job}
  {}{Senior Machine Learning Research Engineer}{Twitter}{June 2020}{January 2023}{Remote, USA}{
    Technical Lead for the Machine Learning Ethics, Transparency, and Accountability team that owned
    Responsible Machine Learning development and research at Twitter.
    

    \begin{myitemize}

      \item Improved processes, gave technical guidance, mentored other engineers, and led
      organization-wide improvements.

      \item Built a system of feature pipelines and tools for researchers that accelerated critical team
      research by 20x while ensuring more reliable results.

      \item Led projects to build tools into Twitter's internal Tensorflow Extended ecosystem that enabled teams to
      rapidly identify undue biases and weaknesses in model performance.

      \item Helped push adoption of team work, leading to company-wide adoption of our model quality metrics and tools. Presented work in multiple forums.
      \autocite{twitter_htl_racial_bias,twitter_recsys_distributional_inequality,facct_2022_talk,datascience_2022_talk,privacy_enchancing_tech_post}

      \item Continued service on company advisory groups, including efforts to select a new Twitter-wide data processing stack that would 
      lead to 3-5x speedups in key data pipelines.

    \end{myitemize}
  }
\end{job}

\begin{job}
  {}{Senior Data Scientist}{Twitter}{July 2017}{June 2020}{Boulder, CO}{
    Data scientist on several teams, most importantly as tech lead for the Health Data Science team,
    which worked on integrity, combating abuse, identifying fake accounts, and studying misinformation problems.
    

    \begin{myitemize}
      \item Developed tooling, education, and processes that enabled data scientists to expand and streamline analyses 
      with complex and heterogeneous data sources, which were used by hundreds of data scientists, ML, and data
      engineers weekly.

      \item Developed strategy, model, and data pipeline for identifying potentially compromised accounts.

      \item Developed open-source client libraries for Twitter API products,
      which were used by thousands of API customers
      \autocite{search_tweets_python,do_more_with_twitter_data}.

      \item Built risk model for developers wanting to use Twitter APIs, and model for identifying clusters of
      applications abusing Twitter's API rate limits, allowing programmatic remediation.

      \item Served on company advisory groups for data architecture, open-source software, Python development,
      and as a global lead for Twitter's Hispanic/Latinx employees resource group.

    \end{myitemize}
  }
\end{job}

\begin{job}
  {}{Data Scientist}{Tripadvisor}{July 2016}{July 2017}{Greater Boston Area, MA}{
    Built scalable ML models for the Vacation Rentals group.
    \begin{myitemize}
      \item Designed and built a computer vision feature engineering system that
      includes models to detect humans, extract content, and rate aesthetic
      quality of all photo assets, increasing a primary click-through rate
      metric by 4.8\% and increase in revenue from ad expenditures by 10.4\%.

      \item Built a language model and interface that enables natural-language queries (e.g.\ ``girls getaway'') to find
      collections of destinations, which led to a \textbf{6.1\% improvement} in a primary metric and was
      used by many teams.

      \item Developed language-modeling tools to extract high-information snippets from reviews to display on
      search-result pages to boost SEO rankings.

      \item Developed a common team codebase providing shared tools, common access methods, and other utility
      code that allowed data scientists and engineers to get up-to-speed more quickly and iterate
      faster on projects.
    \end{myitemize}
  }
\end{job}

%----------------------------------------------------------------------------------------
%	Education
%----------------------------------------------------------------------------------------

\section*{Education}
\begin{edu}{Master of Science, Computer Science}{2016}{University of New Mexico}
\end{edu}
\begin{edu}{Bachelor of Science, Psychology}{2010}{University of New Mexico}
\end{edu}

\section*{Technical Skills}

\begin{skilltype}
  {Languages}{Python, SQL, shell, Scala}
\end{skilltype}
\begin{skilltype}
  {ML/Data/AI frameworks}{Spark, Tensorflow, Kubeflow, TFX, Pytorch, Pandas, scikit-learn, Keras, vllm, Ray}
\end{skilltype}

\begin{skilltype}
  {Dev and ML Ops frameworks/platforms}{Google Cloud, Coreweave, Oracle Cloud, Kubernetes, Helm, Airflow, Bazel}
\end{skilltype}


\section*{Selected Publications and Artifacts}
  
  %%%%%%%%%%%%% . else non CV
  \newrefcontext[sorting=chronological]
  \nocite{network_induced_memory_contention,
    % comp_brain_phenotyping_paper,
    skullstrip,do_more_with_twitter_data} \leavevmode\printbibliography[heading=none,keyword={selected}] 
    

\end{document}
